Fluid structure interaction with ETVF

### 2021-10-22 manuscript/paper.tex
Update to new files. Working UDL simulation.

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}

@@

% =========================================
% =========================================
% start
% =========================================

\subsection{Hydrostatic water column on an elastic plate}
\label{sec:results:hstank-elastic-plate}

In this problem we check the accuracy and stability-preserving property of the
proposed scheme in handling the fluid structure interaction. This problem has
been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
analytical solution derived in Li et al. (2015).

We can see the problem description in figure XXX. The water column height is
2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
the bottom of the tank.The material properties of the aluminum are as follows,
a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
sides. Once the simulation begins, a sudden hydrostatic pressure force is
applied on the aluminum plate. With time the plate oscillates and comes to
rest. We compare the static displacement of the plate with the analytical
solution.

In the current simulation a total of two particle spacing is used. One with
$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
XXX we show the final positions of the particles with different particle
resolutions. The fluid contours are pressure and the structure contours is the
y-displacement. In figure XXX we plot the midpoint deflection with time and
compare it with the analytical solution provided by khayyer . It can be seen
that the results produced by the current scheme are accurate and validates the
scheme for further use in FSI problems. We have run a convergence analysis
with a reducing spacing and as can be seen in the figure, that as the particle
spacing is reduced the error is reduced.

Also analyse any other extra plots you are planning to put.

% =========================================
% end
% =========================================

Currently this is a sub problem of elastic dam break. In that problem we are
simulating gate with out considering the gravity. By considering the gravity
we get float division error. It will be interesting to see why such thing is
happening only in the case with gravity and solving such is fun.

\subsection{Hydrostatic water column on an elastic plate}
\label{sec:hydrostatic-water-column-on-an-elastic-plate}

In this problem we check the accuracy and stability-preserving property of the
proposed scheme in handling the fluid structure interaction. This problem has
been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
analytical solution derived in Li et al. (2015).

We can see the problem description in figure XXX. The water column height is
2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
the bottom of the tank.The material properties of the aluminum are as follows,
a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
sides. Once the simulation begins, a sudden hydrostatic pressure force is
applied on the aluminum plate. With time the plate oscillates and comes to
rest. We compare the static displacement of the plate with the analytical
solution.

In the current simulation a total of two particle spacing is used. One with
$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
XXX we show the final positions of the particles with different particle
resolutions. The fluid contours are pressure and the structure contours is the
y-displacement. In figure XXX we plot the midpoint deflection with time and
compare it with the analytical solution provided by khayyer. It can be seen
that the results produced by the current scheme are accurate and validates the
scheme for further use in FSI problems. We have run a convergence analysis
with a reducing spacing and as can be seen in the figure, that as the particle
spacing is reduced the error is reduced.

Also analyse any other extra plots you are planning to put.

@@

\subsection{Static test to test Structure formulation}
\label{sec:static-test}

In \citet{hwang2015development} has a static test where a cantilever beam is
acted upon by a constant load at the tip.

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\usepackage[section]{placeins}

@@

% =========================================
% =========================================
% start
% =========================================
% =========================================
\subsection{Hwang 2014 static cantilever beam}
\label{sec:hwang-2014-static-cantilever-beam}
Currently this is a sub problem of elastic dam break. In that problem we are
simulating gate with out considering the gravity. By considering the gravity
we get float division error. It will be interesting to see why such thing is
happening only in the case with gravity and solving such is fun.

@@

Currently this is a sub problem of elastic dam break. In that problem we are
simulating gate with out considering the gravity. By considering the gravity
we get float division error.

\subsection{Ng 2020 Hydrostatic water column on an elastic plate}
\label{sec:hydrostatic-water-column-on-an-composite-elastic-plate}

This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    % \toprule
    Quantity & Values \\
    % \midrule
    $D$, Diameter & 2m \\
    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
    $c_s$ & 10m/s \\
    $D/\Delta x_{\max}$, lowest resolution & 4 \\
    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
    $C_r$ & 1.08 \\
    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
    Time of simulation & 6 \\
    % \bottomrule
  \end{tabular}
  \caption{Parameters used for the flow past a circular cylinder problem.}%
  \label{tab:fpc-params}
\end{table}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{images/hydrostatic_water_column_on_an_elastic_plate/hydrostatic_water_column_on_an_elastic_plate}
  \caption{Hydrostatic tank}
\label{fig:hs-water-on-plate}
\end{figure}
%
%

\todoin{Comment on the Poisson ratio range of the current scheme}
\todoin{Who did it previously}
\todoin{How to derive the analytical solution in short}
\todoin{Write about the different resolutions}
\todoin{Any other artificial parameters regarding the scheme, alpha, beta}

\todoin{In this problem we check the accuracy and stability-preserving property of the
proposed scheme in handling the fluid structure interaction. This problem has
been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
analytical solution derived in Li et al. (2015).}

The first benchmark test to validate the fluid structure interaction model
corresponds to an elastic plate under a hydrostatic water tank. An elastic
plate of length 1m and width of 5cm is placed under a block of water column of
height 2m is allowed to settle under gravity. The elastic plate is fixed on
both the ends. The material properties of the water are as follows, the
density is 1000 $kg/m^3$, viscosity of $1e-6$. And the material properties of
the elastic plate are as follows, density 2700$kg/m^3$, Young's modulus
$67.5 \times 10^7$ Pa and a Poisson ratio of 0.34. Three different particle
spacing are considered. Initially the fluid is set up with a hydrostatic
pressure distribution as in equation,
%
%
\begin{equation}
  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
\end{equation}
%
%
Once the plate reaches an equilibrium state, the
deflection at the midpoint is compared with the analytical solution,
%
%
\begin{equation}
  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
\end{equation}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:y-disp-hs-water-on-plate}
\end{figure}
%
%
\Cref{fig:y-disp-hs-water-on-plate} depicts the time histories of the plate's
center point deflection with three different particle spacing. From the
presented \Cref{fig:y-disp-hs-water-on-plate} and table \todoin{citetable} we
can see as the particle spacing is reduced the numerical solution by the
current model approaches the analytical model, which proves the convergence
properties of the current scheme. \todoin{compare with other numerical schemes}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:p-hs-tank-elastic-plate}
\end{figure}
%
%
%
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
  \caption{Hydrostatic tank}
\label{fig:sigma-hs-tank-elastic-plate}
\end{figure}

\Cref{fig:p-hs-tank-elastic-plate} shows the pressure distribution in the
fluid domain at different time histories. \Cref{fig:sigma-hs-water-on-plate}
shows the plots of $\sigma_{00}$ distribution of the elastic plate at
different time steps.

\FloatBarrier%

\subsection{Water slamming on a sandwich hull}
\label{sec:water-slamming-on-a-sandwich-hull}
